Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-18 replication_paper/pnas_draft/appendix.Rmd
v1.1 first self contained hopefully

@@

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )

@@

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png", zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png"}}
\end{figure}

@@

```{r python load, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

library(reticulate)
reticulate::py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

@@

@@

@@

fromscratch=False
if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #12161 12162
  n=len(sentences)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #(12103, 768)

@@

ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png}}
\end{figure}
\clearpage

@@

ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png}}
\end{figure}
\clearpage

@@

  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"

@@

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

@@

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_sample_precision_precision.png"}}
\end{figure}
\clearpage

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icb_metro_plot_",thiscrisis,".Rds")

@@

c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x))

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_mids_metro_plot_",thiscrisis,".Rds")

@@

  convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()

  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid() 
  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid() 
  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()

@@

  dim(phoenix_clean) #8,495,402 #3,721,110 #2,813,748 #2912035 #3,508,495 #4,854,787
  phoenix_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") )

@@

  phoenix_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471.tsv")
  dim(phoenix_clean_471)

  phoenix_clean_471 %>%
    unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
    write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471_small.tsv")

@@

  phoenix_clean_196 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196.tsv")
  dim(phoenix_clean_196)

  phoenix_clean_196 %>%
    unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
    write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196_small.tsv")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_",thiscrisis,".Rds")

@@

fromscratch=F
if(fromscratch){
  phoenix_clean <- arrow::read_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") ) 
  c(196, 471) %>% sapply(FUN=function(x) phoenix_barmaps(x))
}

@@

if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
  stop("Missing Terrier event data. See README.")
}

@@

    #terrier_clean_temp %>% saveRDS( here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
    library(arrow) #you have to actually load the library
    terrier_clean_temp  %>%
      arrow::write_parquet(here::here("replication_paper", "data", "ignore", "terrier_clean.parquet") )
}

@@

    icews_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )

>>>>

library(reticulate)
reticulate::py_discover_config()
#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

@@

#pip install -U pip setuptools wheel
#pip install -U spacy
#python -m spacy download en_core_web_sm
library(rvest)

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )

@@

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png", zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png"}}
\end{figure}

@@

@@

import torch
use_cuda = torch.cuda.is_available()
if use_cuda:
    print('__CUDNN VERSION:', torch.backends.cudnn.version())
    print('__Number CUDA Devices:', torch.cuda.device_count())
    print('__CUDA Device Name:',torch.cuda.get_device_name(0))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)

import random
import os
from tqdm.auto import tqdm
import pandas as pd
from transformers import pipeline
from transformers.pipelines.pt_utils import KeyDataset

@@

#Make sure you have a gpu if you want to run thi

@@

fromscratch=False
if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #12161 12162
  n=len(sentences)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #(12103, 768)
else:
  print("Skipping")

@@

ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png}}
\end{figure}
\clearpage

@@

ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png}}
\end{figure}
\clearpage

@@

  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"

@@

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

@@

```{r Stratified Sentence Examples, eval=T, results='hide', echo=F, include=T, message=F, cache=F}

temp <- ICBe_events_agreed_markdown %>% dplyr::select(
  crisno, sentence_span_text,value_markdown,
  act_cooperative , act_deescalate, act_escalate,act_uncooperative,
  interact_decreasecoop,interact_deescalate,
  interact_escalate, interact_increasecoop,
  thinkkind,sayintkind
) %>% pivot_longer(cols=-c(crisno, sentence_span_text,value_markdown)) %>% na.omit() %>% filter(value!='') %>% 
    mutate(value = strsplit(as.character(value), ";")) %>% 
    unnest(value)

temp_sample <- temp %>% mutate(rand=runif(n())) %>% group_by(value)  %>% filter(rand==max(rand)) %>% ungroup() %>% arrange(name, value)

ft_sample_precision_precision1 <- temp_sample %>% 
                                  filter(row_number()<=56) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=8.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((1:56) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png", zoom=1) #

ft_sample_precision_precision2 <- temp_sample %>% 
                                  filter(row_number()>=57) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=8.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((1:59) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png", zoom=1) #

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png"}}
\end{figure}
\clearpage

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/figures/p_icb_metro_plot_",thiscrisis,".Rds")

@@

c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x)) #This just runs every time no from scratch because the files are small

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/figures/p_mids_metro_plot_",thiscrisis,".Rds")

@@

  convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()

  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid() 
  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid() 
  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()

@@

  dim(phoenix_clean) #8,495,402 #3,721,110 #2,813,748 #2912035 #3,508,495 #4,854,787
  phoenix_clean %>% arrow::write_parquet(here::here("git_ignore_folder",  "phoenix_clean.parquet") )

@@

  #phoenix_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471.tsv")
  dim(phoenix_clean_471)

  #phoenix_clean_471 %>%
  #  unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
  #  unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
  #  dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
  #  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471_small.tsv")

@@

  #phoenix_clean_196 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196.tsv")
  #dim(phoenix_clean_196)

  #phoenix_clean_196 %>%
  #  unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
  #  unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
  #  dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
  #  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196_small.tsv")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_lv0_",thiscrisis,".Rds")

@@

fromscratch=F
if(fromscratch){
  phoenix_clean <- arrow::read_parquet(here::here("git_ignore_folder", "phoenix_clean.parquet") ) 
  c(196, 471) %>% sapply(FUN=function(x) phoenix_barmaps(x))
}

@@

@@

    #terrier_clean_temp %>% saveRDS( here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
    library(arrow) #you have to actually load the library
    terrier_clean_temp  %>%
      arrow::write_parquet(here::here("git_ignore_folder", "terrier_clean.parquet") )
}

@@

    icews_clean %>% arrow::write_parquet(here::here("git_ignore_folder", "icews_clean.parquet") )
